---
title: "MBA Starting Salary"
author: "Parv Patni"
date: "December 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
salary.df <- read.csv(paste("MBA Starting Salaries Data.csv",sep = ""))
library(psych)
describe(salary.df)
```
```{r}
dim(salary.df)
head(salary.df)
```

## Plots

```{r}
hist(salary.df$age, breaks=20,col="khaki",xlab="Age in years", main="Graph showing age distribution")
```

```{r}
salary.df$sex=factor(salary.df$sex, levels=c(1,2), labels=c("Male","Female"))
plot(salary.df$sex,col = "skyblue",main = "Gender distribution")
```

```{r}
hist(salary.df$work_yrs, breaks=20,col="green",xlab="Work Experience in years", main="Work experience distribution")
```

```{r}
hist(salary.df$gmat_tot, breaks=40,col="red",xlab="score out of 800", main="Gmat Score distribution")
```

```{r}
salary.df$frstlang = factor(salary.df$frstlang, levels=c(1,2), labels=c("English","Others"))
plot(salary.df$frstlang,col="cyan",main = "Language Distribution")
```

New Structure of Dataset after changing age and first language Data Type
```{r}
str(salary.df)
```

## Dividing dataset into Placed, Not placed, 999, 998

who got placed and disclosed their salary
```{r}
placed.df<-salary.df[which(salary.df$salary>999),]
View(placed.df)
dim(placed.df)
```

Who did not get placed and disclosed
```{r}
unplaced.df<-salary.df[which(salary.df$salary==0),]
View(unplaced.df)
dim(unplaced.df)
```

Who did not answer the survey(998)
```{r}
notsurveyed.df<-salary.df[which(salary.df$salary==998),]
View(notsurveyed.df)
dim(notsurveyed.df)
```

Who answered the survey but did not disclose salary data
```{r}
notdisclosed.df<-salary.df[which(salary.df$salary==999),]
View(notdisclosed.df)
dim(notdisclosed.df)
```

Summing all the 4 sub catagories(103+90+46+35)  
```{r}
dim(notdisclosed.df)[1]+dim(placed.df)[1]+dim(unplaced.df)[1]+dim(notsurveyed.df)[1]
```

We get a total of 274 wich is equal to our original dimensions

Summary of Placed 
```{r}
describe(placed.df)
```

Average Salary of a placed Grad is 103030.74

```{r}
boxplot(placed.df$salary, horizontal = TRUE, main="Salary", col="darkolivegreen1")
```
```{r}
boxplot(placed.df$age, horizontal = TRUE, main="age distribution for placed Grad", col="darkolivegreen1")
```
```{r}
boxplot(placed.df$work_yrs, horizontal = TRUE, main="Work experience of placed Grad", col="darkolivegreen1")
```

## Comparison of Salary with Work Experience

```{r}
library(car)
scatterplot(x = placed.df$salary , y = placed.df$work_yrs, main="comparison of salaries with work experience" , ylab="Work years", xlab="Salary")
```

## Comparison of Salary with age

```{r}
scatterplot(x = placed.df$salary , y = placed.df$age, main="comparison of salary with ages", xlab="Salary", ylab="Age")
```

## Comparison of Salary with Gmat Score

```{r}
scatterplot(x = placed.df$salary , y = placed.df$gmat_tot, main="comparison of salary with Gmat Score", xlab="Salary", ylab="Gmat Score")
```

## Comparing different factors that affect starting salaries

```{r}
a <- xtabs(~salary + sex + work_yrs, data = placed.df)
ftable(a)
```

```{r}
aggregate(salary~age, data=placed.df,FUN = "mean")
```
```{r}
aggregate(salary~satis, data = placed.df, FUN = "mean")
```
It shows that nobody placed has a lower satisfaction level of 1 or 2

Let's take some hypothesis

```{r}
mytable1 <-xtabs(~salary+work_yrs,data=placed.df)
chisq.test(mytable1)
```

Since p<0.01 there is a relationship betweeen work experience and salary

```{r}
mytable2<-xtabs(~salary+frstlang,data=placed.df)
chisq.test(mytable2)
```

Since p<0.01 we can say that there is a relationship between first language and salary

```{r}
mytable3<-xtabs(~salary+gmat_tot,data=placed.df)
chisq.test(mytable3)
```

Since p<0.01 we see there exists a relationship between Total GMAT score and starting salary.

```{r}
library(corrgram)
corrgram(salary.df,upper.panel = panel.pie, main="Corrgram of Starting Salaries intercorrelations")
```

##linear regression models

model1:
linear model taking age , gmat performance and expereince for consideration indeciding starting salary of mba graduates
```{r}
fit <- lm( salary~age+gmat_tpc+work_yrs,data=placed.df)
summary(fit)
```

model2:
linear model taking age,gender, gmat performance and expereince for consideration indeciding starting salary of mba graduates

```{r}
fit <- lm( salary~age+gmat_tpc+work_yrs+sex,data=placed.df)
summary(fit)
```

model3:
linear model taking age,first language, gmat performance and expereince for consideration indeciding starting salary of mba graduates

```{r}
fit <- lm( salary~age+gmat_tpc+work_yrs+frstlang,data=placed.df)
summary(fit)
```

model4:
linear model taking job satisfaction, work experience, first language for consideration indeciding starting salary of mba graduates
```{r}
fit <- lm( salary~satis+work_yrs+frstlang,data=placed.df)
summary(fit)
```

work_yrs and frstlang are significant variables in this model. The multiple R squared value indicates that the model accounts for 24.66% of the variance in the variables The residual error(15740) can be thought of as the average error in predicting salary using work experience, job satisfaction and first language.

```{r}
 chisq.test(unplaced.df$work_yrs,unplaced.df$satis)
```

Therefore, students with work experience and unplaced are satidfied with MBA program